\documentclass[10pt]{article}

% ---------- PACKAGES ----------
\usepackage[margin=0.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage[none]{hyphenat}

% ---------- SECTION STYLES ----------
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=2pt}
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}

% ---------- DOCUMENT ----------
\begin{document}

% ---------- HEADER ----------
\begin{center}
    {\huge \textbf{Connor Love}}\\[4pt]
    \footnotesize
    \begin{tabular}{@{}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{}}
      \href{mailto:love.563@buckeyemail.osu.edu}{love.563@buckeyemail.osu.edu} &
      (216) 318-4899 &
      \href{https://linkedin.com/in/connorlove2005/}{linkedin.com/in/connorlove2005/} &
      \href{https://github.com/loveconnor}{github.com/loveconnor} &
      \href{https://connorlove.com}{connorlove.com}
    \end{tabular}
\end{center}

% ---------- PROFILE ----------
\section*{Profile}
Student researcher and software engineer (OSU CSE) with experience in \textbf{web application development for data handling and monitoring}. Skilled in TypeScript, React, Node.js, PostgreSQL, and Docker. Passionate about applying scalable backend systems, data visualization, and accessible UIs to support \textbf{vehicle health, maintenance, and operations tracking}. Available Autumn 2025.

% ---------- EDUCATION ----------
\section*{Education}
\textbf{The Ohio State University} \hfill Columbus, OH \\
Bachelor of Science, Computer Science and Engineering \hfill Expected May 2028 \\[6pt]

\textbf{Kent State University} \hfill Kent, OH \\
Aug. 2024 -- Jul. 2025 \\
GPA: 3.98 \quad | \quad Choose Ohio First Scholar (2024--2025) \\

% ---------- RESEARCH ----------
\section*{Research Experience}
\textbf{Choose Ohio First Scholar -- Student Researcher} \hfill Kent State University \\
Aug. 2024 -- Jul. 2025
\begin{itemize}
    \item Conducted research on \textbf{Spatial Social Networks}, developing efficient algorithms for keyword-based community search (KCS-SSN).
    \item Built an interactive GUI to \textbf{query, filter, and visualize} high-cohesion communities; iterated with faculty feedback.
    \item Awarded a competitive STEM scholarship and presented results at the Kent State University Conference (Apr 2025).
\end{itemize}

% ---------- PROJECTS ----------
\section*{Projects}
\textbf{EduSynapse} \hfill TypeScript, Node.js, PostgreSQL, Docker, Tailwind CSS
\begin{itemize}
    \item Architected a \textbf{data-centric learning platform} with PostgreSQL and Docker for reproducible deployments.
    \item Built dashboards and components for \textbf{progress and health tracking}, generalizable to fleet monitoring applications.
    \item Implemented \textbf{role-appropriate accessibility} and error-state handling for reliability.
\end{itemize}

\textbf{LoveChat} \hfill TypeScript, React, Tailwind CSS, Markdown, PostgreSQL
\begin{itemize}
    \item Developed a full-stack application with \textbf{streamed data workflows} and persistent storage, applicable to telemetry and incident review.
    \item Implemented advanced search, filtering, and pagination to support large-scale data handling.
    \item Delivered responsive layouts and collaboration features while maintaining performance.
\end{itemize}

\textbf{Freelance Web Applications} \hfill Creative Developer
\begin{itemize}
    \item Designed and deployed \textbf{3+ responsive dashboards and portals}, improving community outreach and client operations.
    \item Shipped modern applications with authentication, CRUD flows, and \textbf{audit-friendly activity logs}.
\end{itemize}

% ---------- PROFESSIONAL ----------
\section*{Professional Experience}
\textbf{Telecommunications Intern} \hfill Modern Telecom -- Medina, OH \\
Summer 2024
\begin{itemize}
    \item Configured and deployed \textbf{50+ VoIP phones} for small businesses, ensuring smooth installation and reliable communications.
    \item Assisted in network deployment and troubleshooting in client-facing environments.
\end{itemize}

\textbf{Freelance Creative Developer} \hfill Remote \\
2023 -- Present
\begin{itemize}
    \item Delivered full-cycle projects: requirements gathering, UI/UX design, frontend/backend development, deployment, and client training.
    \item Specialized in \textbf{scalable, data-driven web applications} aligned with real-world operations monitoring.
\end{itemize}

% ---------- HONORS ----------
\section*{Honors \& Awards}
\textbf{3rd Place} -- Kent Hack Enough Hackathon (Feb 2025), EduSynapse Project \\
\textbf{Choose Ohio First Scholar} -- Competitive STEM Research Scholarship (2024--2025) \\

% ---------- SKILLS ----------
\section*{Technical Skills}
\textbf{Web \& Data for Monitoring Apps:} TypeScript, React, Next.js, Node.js, PostgreSQL, REST APIs, Docker \\
\textbf{Languages:} JavaScript, Java, C++, Python, SQL, HTML/CSS \\
\textbf{UI/UX:} Tailwind CSS, Material-UI, accessibility best practices \\
\textbf{Dev \& Design:} Git, Vercel, Figma, Photoshop, Illustrator \\
\textbf{AI/Integrations:} OpenAI API, Google Gemini, Claude, ElevenLabs \\

% ---------- PORTFOLIO ----------
\section*{Portfolio}
Portfolio of research and projects: \href{https://connorlove.com}{https://connorlove.com}

\end{document}
