\documentclass[10pt]{article}

% ---------- PACKAGES ----------
\usepackage[margin=0.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{tabularx}

% ---------- SECTION STYLES ----------
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=2pt}
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}

\begin{document}

% ---------- HEADER ----------
\begin{center}
  {\huge \textbf{Connor Love}}\\[4pt]
  \footnotesize
  \begin{tabular}{@{}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{}}
    \href{mailto:loveconnor2005@gmail.com}{loveconnor2005@gmail.com} &
    (216) 318-4899 &
    \href{https://linkedin.com/in/connorlove2005/}{linkedin.com/in/connorlove2005/} &
    \href{https://github.com/coding-with-love}{github.com/coding-with-love} &
    \href{https://connorlove.com}{connorlove.com}
  \end{tabular}
\end{center}

% ---------- EDUCATION ----------
\section*{Education}
\textbf{The Ohio State University} — Columbus, OH\\
Bachelor of Science, Computer Science and Engineering \,|\, Expected May 2028

\vspace{4pt}
\textbf{Kent State University} — Kent, OH \hfill Aug. 2024 – Jul. 2025
\begin{itemize}
  \item Computer Science Coursework
  \item GPA: 3.98
  \item Choose Ohio First Scholar (2024–2025)
\end{itemize}

% ---------- RESEARCH & SCHOLARSHIPS ----------
\section*{Research \& Scholarships}
\textbf{Choose Ohio First Scholar – Kent State University (2024–2025)}
\begin{itemize}
  \item Awarded competitive scholarship supporting STEM majors.
  \item Conducted research on Spatial Social Networks, focusing on keyword-based community search over spatial-social networks (KCS-SSN).
  \item Designed efficient algorithms and developed a user-friendly GUI to retrieve communities with high social and spatial cohesiveness.
  \item Presented research poster at the Kent State University Conference (Apr 2025).
\end{itemize}

% ---------- HONORS & COMPETITIONS ----------
\section*{Honors \& Competitions}
3rd Place – Kent Hack Enough Hackathon (Feb 2025) – EduSynapse Project

% ---------- PROJECTS ----------
\section*{Projects}

\textbf{EduSynapse} \,|\, TypeScript, Node.js, PostgreSQL, Docker, Tailwind CSS
\begin{itemize}
  \item Built an AI-driven education platform featuring adaptive learning paths, real-time code execution, and knowledge mapping.
  \item Improved learner engagement with smart review tools and an always-available AI tutor.
\end{itemize}

\textbf{LoveChat} \,|\, TypeScript, React, Tailwind CSS, Markdown, PostgreSQL
\begin{itemize}
  \item Created an advanced AI chat application with multi-model integration, reasoning features, and dynamic workflows.
  \item Enhanced accessibility and productivity through real-time web search, text-to-speech, and artifact/code preservation.
  \item Showcased innovation with customizable personas, automation tools, and collaboration features.
\end{itemize}

% ---------- EXPERIENCE ----------
\section*{Experience}
\textbf{Freelance Creative Web Designer/Developer}
\begin{itemize}
  \item Built and deployed 3+ websites for local organizations, helping them establish an online presence and improve community outreach.
  \item Delivered modern, responsive designs that balanced usability with creative branding.
\end{itemize}

\textbf{Telecommunications Intern — Modern Telecom — Medina Ohio}
\begin{itemize}
  \item Assisted in configuring and deploying 50+ VoIP phones for small businesses, ensuring seamless installation and on-site technical support.
  \item Onsite installation and support
\end{itemize}

% ---------- TECHNICAL SKILLS ----------
\section*{Technical Skills}
\textbf{Languages:} TypeScript, JavaScript, Java, C++, Python, SQL, HTML/CSS

\vspace{2pt}
\textbf{Frameworks \& Libraries:} React, Next.js, Three.js, GSAP, Framer Motion, Tailwind CSS, Material-UI

\vspace{2pt}
\textbf{Backend \& Database:} Node.js, Supabase, PostgreSQL, REST APIs

\vspace{2pt}
\textbf{Tools \& Platforms:} Docker, Vercel, Figma, Photoshop, Illustrator

\vspace{2pt}
\textbf{AI \& Integrations:} OpenAI API, Google Gemini, Claude, ElevenLabs, Serper API

\end{document}
