\documentclass[10pt]{article}

% ---------- PACKAGES ----------
\usepackage[margin=0.4in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{tabularx}

% ---------- SECTION STYLES ----------
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=2pt}
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}

\begin{document}

% ---------- HEADER ----------
\begin{center}
  {\huge \textbf{Connor Love}}\\[4pt]
  \footnotesize
  \begin{tabular}{@{}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{\hspace{0.8em}\textbar\hspace{0.8em}}c@{}}
    \href{mailto:loveconnor2005@gmail.com}{loveconnor2005@gmail.com} &
    (216) 318-4899 &
    \href{https://linkedin.com/in/loveconnor/}{linkedin.com/in/loveconnor/} &
    \href{https://github.com/loveconnor}{github.com/loveconnor} &
    \href{https://connorlove.com}{connorlove.com}
  \end{tabular}
\end{center}

% ---------- EDUCATION ----------
\section*{Education}
\textbf{The Ohio State University} — Columbus, OH\\
Bachelor of Science, Computer Science and Engineering \,|\, Expected May 2028

\vspace{4pt}
\textbf{Kent State University} — Kent, OH
\begin{itemize}
  \item Computer Science Coursework
  \item GPA: 3.98
  \item Aug. 2024 - Jul. 2025
\end{itemize}

% ---------- RESEARCH & SCHOLARSHIPS ----------
\section*{Research \& Scholarships}
\textbf{Choose Ohio First Scholar – Kent State University (2024–2025)}
\begin{itemize}
  \item Awarded competitive STEM scholarship.
  \item Conducted research on keyword-based community search over spatial-social networks; designed algorithms and GUI to identify cohesive communities.
  \item Presented research poster at the Kent State University Conference (Apr 2025).
\end{itemize}

% ---------- HONORS & COMPETITIONS ----------
\section*{Honors \& Competitions}
3rd Place – Kent Hack Enough Hackathon (Feb 2025) – EduSynapse Project

% ---------- PROJECTS ----------
\section*{Projects}

\textbf{LoveCode} \,|\, Next.js, Node.js, Vercel Sandboxes, Tailwind CSS, TypeScript
\begin{itemize}
  \item Built an AI-powered coding platform where users can describe apps in natural language and instantly receive runnable applications with live previews.
  \item Implemented sandboxed execution and real-time developer tools (file diffs, logs, error monitoring, embedded previews).
\end{itemize}

\textbf{LoveChat} \,|\, TypeScript, React, Tailwind CSS, Markdown, PostgreSQL
\begin{itemize}
  \item Created an advanced AI chat application with multi-model integration, reasoning features, and dynamic workflows.
  \item Showcased innovation with customizable personas, automation tools, and collaboration features.
\end{itemize}

% ---------- EXPERIENCE ----------
\section*{Experience}
\textbf{Freelance Creative Web Designer/Developer}
\begin{itemize}
  \item Built and deployed 3+ websites for local organizations, helping them establish an online presence and improve community outreach.
  \item Delivered modern, responsive designs that balanced usability with creative branding.
\end{itemize}

\textbf{Full Stack Engineering Intern — Currents Systems Inc (DBA Visor) — Remote (Ohio)}
\begin{itemize}
  \item Developing interactive data visualizations, including a filterable scatter plot interface for large datasets.
  \item Building and maintaining full stack features in a production engineering environment.
  \item Utilizing approved AI tools to generate and process stock vehicle imagery while adhering to company IP and data security policies.
  \item Collaborating directly with the CTO in a remote, part-time engineering role alongside academic commitments.
\end{itemize}

\textbf{Contract Software Developer — Independent Contractor — Remote (Ohio)}
\begin{itemize}
  \item Providing ongoing, project-based software and web development services on an as-needed basis.
  \item Implementing features, debugging issues, and maintaining production systems across client projects.
  \item Delivering technical support, code integration, and documentation while operating as an independent contractor.
\end{itemize}


% ---------- TECHNICAL SKILLS ----------
\section*{Technical Skills}
\textbf{Languages:} TypeScript, JavaScript, Java, C++, Python, SQL, HTML/CSS

\vspace{1pt}
\textbf{Frameworks \& Libraries:} React, Next.js, Three.js, GSAP, Framer Motion, Tailwind CSS, Material-UI

\vspace{1pt}
\textbf{Backend \& Database:} Node.js, Supabase, PostgreSQL, REST APIs

\vspace{1pt}
\textbf{Tools \& Platforms:} Docker, Vercel, Figma, Photoshop, Illustrator

\vspace{1pt}
\textbf{AI \& Integrations:} OpenAI API, Google Gemini, Claude, ElevenLabs, Serper API

\end{document}
